\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
fixed quotation marks, removed a few unnecessary spaces

There has been relatively little examination of how human observers perceive robot arm trajectories in environments with obstacles. There is no data available for how human observers react to such robot motions. It is not clear whether minimum-jerk trajectories (or other cost functions) are the best descriptors of motions in such environments or if there are other features that better explain human-observer preferences in such sitations. Our goal in this work is to collect the data needed to answer the query, "Which robot trajectories in cluttered environments do human-observers prefer". A second question that we would like to answer is "Why are certain robot trajectories preferred by human-observers?". This is a larger question that we aim to address in future work and instead we focus on,"Can we predict a human-observer preference for a given trajectory". The answer to this latter question, we hope, will eventually point us towards trajectories that are better accepted by human observers.

@@

The first set of features we compute for each trajectory take into account the environment around the robot, the shape of the trajectory and the dynamics of the trajectory. These make up our unary features computed only on the input trajectory. We also include features that compare each trajectory to a nominal trajectory - these feature serve to characterize how much the trajectory deviates from the "expected" path. We go over the multi-point features in the next section. First, we detail the features we computed on each trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$. Note that our features are generic, i.e. they can be computed in the same manner for any robot arm trajectory. We believe that our methods should be easily extensible to robots other than the PR2 as well and individual trajectory classifiers could be built for each different robot arm in a similar manner.

{\bf Path length:}
%The length of the trajectory \tj{} computed as the sum over trajectory segments of the euclidean distance between end points of the segment, or
%\begin{equation}
%\text{Length} = \sum_{i=0}^{n-1} \| q_\text{i}-q_\text{i+1} \|
%\end{equation}
We compute path length for the joint-space trajectory and for three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links of the right arm (the moving arm). We also compute the length of the trajectory in angular distance by summing over the waypoints $\arccos( \langle Q_\text{i},Q_\text{i+1}\rangle^2-1 )$ where $Q_\text{i}$ is the quaternion orientation for the $i$-th waypoint (referred to later as the "quat\_dist" feature).

>>>>

There has been relatively little examination of how human observers perceive robot arm trajectories in environments with obstacles. There is no data available for how human observers react to such robot motions. It is not clear whether minimum-jerk trajectories (or other cost functions) are the best descriptors of motions in such environments or if there are other features that better explain human-observer preferences in such sitations. Our goal in this work is to collect the data needed to answer the query, ``Which robot trajectories in cluttered environments do human-observers prefer'' A second question that we would like to answer is ``Why are certain robot trajectories preferred by human-observers?'' This is a larger question that we aim to address in future work and instead we focus on, ``Can we predict a human-observer preference for a given trajectory'' The answer to this latter question, we hope, will eventually point us towards trajectories that are better accepted by human observers.

@@

The first set of features we compute for each trajectory take into account the environment around the robot, the shape of the trajectory and the dynamics of the trajectory. These make up our unary features computed only on the input trajectory. We also include features that compare each trajectory to a nominal trajectory - these feature serve to characterize how much the trajectory deviates from the ``expected'' path. We go over the multi-point features in the next section. First, we detail the features we computed on each trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$. Note that our features are generic, i.e. they can be computed in the same manner for any robot arm trajectory. We believe that our methods should be easily extensible to robots other than the PR2 as well and individual trajectory classifiers could be built for each different robot arm in a similar manner.

{\bf Path length:}
%The length of the trajectory \tj{} computed as the sum over trajectory segments of the euclidean distance between end points of the segment, or
%\begin{equation}
%\text{Length} = \sum_{i=0}^{n-1} \| q_\text{i}-q_\text{i+1} \|
%\end{equation}
We compute path length for the joint-space trajectory and for three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links of the right arm (the moving arm). We also compute the length of the trajectory in angular distance by summing over the waypoints $\arccos( \langle Q_\text{i},Q_\text{i+1}\rangle^2-1 )$ where $Q_\text{i}$ is the quaternion orientation for the $i$-th waypoint (referred to later as the ``quat\_dist'' feature).
